The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-13 thesis/paper.tex
Notes in disc

@@

>>>>

\usepackage{url}

@@

Implications for Practice tips: 
       3. Each implications for practice section should include descriptions of a) problematic issue(s) being addressed, b) the specific audience(s) to which implications are addressed, c) a small number of recommendations about what the audience should/could/should not do based on the research findings, d) an expected outcome of carrying out recommendation(s), and e) some specific illustrations of what carrying out the recommendations might look like, perhaps in narrative form.

\url{https://www.princeton.edu/futureofchildren/publications/journals/article/index.xml?journalid=46&articleid=212&sectionid=1379}
